%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Software Developer} % Job title
    {DHIS-2 (University Of Oslo)} % Organization
    {Oslo, Norway} % Location
    {Oct 2015 - PRESENT} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Working with open source health management information system DHIS2.}
        \item {Developed RESTful APIs for Collection, Processing and Analysis of patients data.}
        \item {Design and implementation of SMS Module for event and schedule based notifications.}
        \item {Leading the move for Data Collection through SMS which enables people working at remote village level to capture and send disease surveillance data.}
        \item {API development to expose SMS resources to integrate other parallel systems.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Ericsson Integration Consultant} % Job title
    {Ericsson Iraq} % Organization
    {Sulaymania, Iraq} % Location
    {Jan. 2013 - Jun. 2014} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Developed customizations for Customer Life Cycle Management, Credit Control Management, Rating and Discount Plans, Retail-Interconnect Billing.}
        \item {Handling customization in BSS domain (CRM, Billing System).}
        \item {Develop detailed requirements for OCS (Online Charging System) Service provisioning consolidation and conduct complete impact analysis including Developing and Maintaining Consolidated Customer Profile, VAS Provisioning on In-house 3rd Party platforms, Refills, Package Plan Change and Content Purchase.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Ericsson Integration Consultant} % Job title
    {Ericsson Pakistan} % Organization
    {Islamabad, Pakistan} % Location
    {Aug. 2011 - Apr. 2013} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {End-to-End solution design for Shared Accounts (Master/Subordinate), MNP (Mobile Number Portability) support, DDS (Dynamic Discount Solution), E-topup (Electronic Recharge), LBS (Location Based Services).}
        \item {Design and implementation of Rating/Discount plans which involved Offer Driven Rating, Periodic Account Management, Timer Offers, Composite DA, IPF (DDS), Product Private DA, and Multiple Purchase of Products, USSD, FAF and Community Charging.}
        \item {Design Voucher Based and Voucher Less Recharges, BOR, USSD notifications.}
        \item {Ericsson OCS Integrations with Teklec CORE, HLR (Huawie Packet Core), GGSN (Huawei), USSD CallBack (OpenCode), and OSS (Ericsson)}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Ericsson Integration Consultant} % Job title
    {Ericsson Pakistan} % Organization
    {Lahore, Pakistan} % Location
    {Aug. 2007 - Apr. 2010} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {RTCFA (Real Time Charging For All) Implementation.}
        \item {OCS (INAP) Integration with CORE network STP,HLR.}
        \item {Database integriton with USSD/MAP servers}
        \item {Voucher Managment and thrid party Customer Administration System.}
        \item {OCS Integration with DDS (Dynamic Discount Solution) by Digitata.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Integration Engineer} % Job title
    {Ericsson Iran} % Organization
    {Tehran, Iran} % Location
    {Sep. 2009 - Dec. 2009} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Ericsson OCS Network/System Upgrade for MTNIrancell.}
        \item {Development and Implementation of customizations based on customer requirements.}
        \item {Network upgrade from legacy SS7 to SIGTRAN for high speed availability.}
      \end{cvitems}
    }
%---------------------------------------------------------
\end{cventries}
